Modelling Stochastic Time Delay for Regression

### 2021-03-21 documentation/article/article.tex
Refine related work section.

\section{Related Work}
There is extensive literature on time series problems with time delay dependencies. In the statistical literature there a number of treatments which focus on 
fixed time delay dependencies. For example, Granger Causality is used to determine whether one time series is useful for forecasting another, across some fixed delay.
Distributed Lag and Dynamic Regression models are able to handle linear and non-linear cause/effect relations that exist across multiple time lags.
Nonetheless, these models assume a fixed time lag dependency.

@@

The field of system identification has a variety of literature on dynamic non-linear systems. For example, the NARMAX model can be used to identify 
non-linear systems with fixed time delays between input and output. At the same time, there are also treatments on systems with disturbances in the input, known as EIV systems. To our knowledge,
these works do not deal with uncertainty in the time domain.

Finally, recent literature such as Dynamic Time Lag Regresion and Variable Lag Granger causality deal with non-stationary time lag dependencies. In other words, the lag structure is assumed to evolve over time.

There has been relatively little work on \emph{stochastic time delays} i.e. time delays which vary randomly. In this paper, we deal with this specific case.

>>>>

\section{Related Work}
There is extensive existing literature on time series problems with time delay dependencies. In the statistical disciplines there a number of treatments which focus on 
fixed time delay dependencies. For example, Granger Causality is used to determine whether one time series is useful for forecasting another, across some fixed delay.
Distributed Lag and Dynamic Regression models are able to handle linear and non-linear cause and effect relations that exist across multiple time lags.
Nonetheless, these models assume a fixed time lag dependency.

@@

The field of system identification also has considerable literature on dynamic non-linear systems. For example, the NARMAX model can be used to identify 
non-linear systems with fixed time delays between input and output. At the same time, there are also treatments on systems with disturbances in the input, known as EIV systems. To our knowledge,
these works do not deal with uncertainty in the time domain.

Finally, recent papers such as Dynamic Time Lag Regression and Variable-Lag Granger Causality deal with non-stationary time lag dependencies. In other words, the lag structure is assumed to evolve over time.

There has been little work on \emph{stochastic time delays} i.e. time delays which vary randomly. In this paper, we deal with this specific case.
